### 2023-12-30 tesis_Ashish/Chapter7/chapter7.tex
Updated thesis 30 Dec 2023

The Phase II upgrade of the CMS Tracker is a crucial project undertaken to maintain the effectiveness of the CMS experiment during the High Luminosity LHC (HL-LHC) phase, which is expected to start in 2029. The HL-LHC will significantly increase the instantaneous luminosity, leading to a higher number of proton-proton collisions per bunch crossing. Instantaneous luminosity will increase to an unprecedented value of $7.5 \times 10^{34} cm^{-2} \: s^{-1}$ which corresponds to 200 proton-proton collisions per bunch crossing. This higher collision rate poses several challenges, including increased radiation levels, higher data rates, and more complex event environment. Run 2 pixel detector will not be able to handle these extreme radiation environment, resolve nearby particle tracks and operate properly to give a reliable estimate of the instantaneous luminosity for such a high pileup. That is why it will be replaced by a new pixel detector. The Phase II upgrade of the CMS tracker comprises of two main components: the Inner Tracker (IT) and the Outer Tracker (OT) \cite{collaboration:2759074}. The Inner Tracker consists of three main sub-components: the Tracker Endcap Pixel detector (TEPX), the Tracker Forward Pixel detector (TFPX), and the Tracker Barrel Pixel (TBPX) detector as shown in Fig. \ref{fig:Innertracker} \cite{CERN-LHCC-2017-009}.  %The Outer Tracker is responsible for detecting charged particles in the outer region of the CMS detector. It consists of two key subsystems: the silicon strip tracker and the silicon macro pixel tracker \cite{RoyChowdhury:2729279}.

@@

\begin{table}[htbp]
  \centering
  \caption[Expected stat. precision of TEPX under low pileup] {Expected statistical precision (in $\%$) in head-on collisions during typical vdM conditions with pileup of 0.5 for TEPX clusters and two-fold coincidences over different integration time period \cite{Collaboration:2759074}.}
\begin{tabular}{lcccc}
vdM (PU 0.5) & Trigger Rate (kHz) & 1 bx, 1s & 1 bx, 30s\\
\hline
TEPXD4R1 Clusters&1000&1.82&0.332\\
TEPXD4R1 2x Coincidences in phi &1000&5.98&1.09\\
TEPXD4R1 2x Coincidences in r &1000&11.1&2.02\\
TEPXD4R1 2x Coincidences &1000&5.27&0.962\\
TEPX Clusters&500&0.709&0.129\\
TEPX 2x Coincidences in phi &500&2.65&0.485\\
TEPX 2x Coincidences in r &500&4.59&0.838\\
TEPX 2x Coincidences &500&2.3&0.42\\
\end{tabular}
\end{table}

\begin{table}[htbp]
\centering
\caption[Expected stat. precision of TEPX under high pileup]{Expected statistical precision (in $\%$) in head-on collisions during physics conditions with pileup of 200 for TEPX clusters and two-fold coincidences over different integration time period \cite{Collaboration:2759074}.}
\begin{small} % this command will decrease the font size
\begin{tabular}{lcccc}
Algorithm & Trigger Rate (kHz) & 1 bx, 1s & 2500 bx, 1s\\
\hline
TEPXD4R1 Clusters & 825 & 0.1 & 0.002  \\
TEPXD4R1 2x Coincidences in phi & 825 & 0.329 & 0.00659 \\
TEPXD4R1 2x Coincidences in r & 825 & 0.61 & 0.0122  \\
TEPXD4R1 2x Coincidences & 825 & 0.29 & 0.0058  \\
TEPX Clusters & 75 & 0.0915 & 0.00183  \\
TEPX 2x Coincidences in phi & 75 & 0.343 & 0.00685 \\
TEPX 2x Coincidences in r & 75 & 0.593 & 0.0119  \\
TEPX 2x Coincidences & 75 & 0.297 & 0.00594  \\
\end{tabular}
\end{small}
\end{table}

>>>>

The Phase II upgrade of the CMS Tracker is a crucial project undertaken to maintain the effectiveness of the CMS experiment during the High Luminosity LHC (HL-LHC) phase, which is expected to start in 2029. The HL-LHC will significantly increase the instantaneous luminosity, leading to a higher number of proton-proton collisions per bunch crossing. Instantaneous luminosity will increase to an unprecedented value of $7.5 \times 10^{34} cm^{-2} \: s^{-1}$ which corresponds to 200 proton-proton collisions per bunch crossing. This higher collision rate poses several challenges, including increased radiation levels, higher data rates, and more complex event environment. Run 2 pixel detector will not be able to handle these extreme radiation environment, resolve nearby particle tracks and operate properly to give a reliable estimate of the instantaneous luminosity for such a high pileup. That is why it will be replaced by a new pixel detector. The Phase II upgrade of the CMS tracker comprises of two main components: the Inner Tracker (IT) and the Outer Tracker (OT) \cite{RoyChowdhury:2729279}. The Inner Tracker consists of three main sub-components: the Tracker Endcap Pixel detector (TEPX), the Tracker Forward Pixel detector (TFPX), and the Tracker Barrel Pixel (TBPX) detector as shown in Fig. \ref{fig:Innertracker} \cite{CERN-LHCC-2017-009}.  %The Outer Tracker is responsible for detecting charged particles in the outer region of the CMS detector. It consists of two key subsystems: the silicon strip tracker and the silicon macro pixel tracker \cite{RoyChowdhury:2729279}.

@@

\begin{table}[htbp]
  \centering
  \caption[Expected stat. precision of TEPX under low pileup] {Expected statistical precision (in $\%$) in head-on collisions during typical vdM conditions with pileup of 0.5 for TEPX clusters and two-fold coincidences over different integration time period \cite{Collaboration:275907420}.}
\begin{tabular}{lcccc}
vdM (PU 0.5) & Trigger Rate (kHz) & 1 bx, 1s & 1 bx, 30s\\
\hline
TEPXD4R1 Clusters&1000&1.82&0.332\\
TEPXD4R1 2x Coincidences in phi &1000&5.98&1.09\\
TEPXD4R1 2x Coincidences in r &1000&11.1&2.02\\
TEPXD4R1 2x Coincidences &1000&5.27&0.962\\
TEPX Clusters&500&0.709&0.129\\
TEPX 2x Coincidences in phi &500&2.65&0.485\\
TEPX 2x Coincidences in r &500&4.59&0.838\\
TEPX 2x Coincidences &500&2.3&0.42\\
\end{tabular}
\end{table}

\begin{table}[htbp]
\centering
\caption[Expected stat. precision of TEPX under high pileup]{Expected statistical precision (in $\%$) in head-on collisions during physics conditions with pileup of 200 for TEPX clusters and two-fold coincidences over different integration time period \cite{Collaboration:275907420}.}
\begin{small} % this command will decrease the font size
\begin{tabular}{lcccc}
Algorithm & Trigger Rate (kHz) & 1 bx, 1s & 2500 bx, 1s\\
\hline
TEPXD4R1 Clusters & 825 & 0.1 & 0.002  \\
TEPXD4R1 2x Coincidences in phi & 825 & 0.329 & 0.00659 \\
TEPXD4R1 2x Coincidences in r & 825 & 0.61 & 0.0122  \\
TEPXD4R1 2x Coincidences & 825 & 0.29 & 0.0058  \\
TEPX Clusters & 75 & 0.0915 & 0.00183  \\
TEPX 2x Coincidences in phi & 75 & 0.343 & 0.00685 \\
TEPX 2x Coincidences in r & 75 & 0.593 & 0.0119  \\
TEPX 2x Coincidences & 75 & 0.297 & 0.00594  \\
\end{tabular}
\end{small}
\end{table}
